### 2019-11-05 article.tex
Initial Overleaf Import

\documentclass{article}

\usepackage{arxiv}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}   % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{lipsum}

\usepackage{longtable}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{setspace}
\usepackage{xcolor}
\usepackage{amsmath}

\title{VIP-193: Committee-Based POA}
\author{
  Ziheng (Peter) Zhou \vspace{1ex}\\
  VeChain Foundation \\
  \texttt{peter.zhou@vechain.com}
  \And
  Zhijie Ren \vspace{1ex} \\
  VeChain Foundation \\
  \texttt{zhijie.ren@vechain.com}
}
\date{}

\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}\vspace{3pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}\vspace{3pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}\vspace{3pt}}m{#1}}

\begin{document}
\maketitle

% \begin{abstract}
% \end{abstract}

% keywords can be removed
% \keywords{First keyword \and Second keyword \and More}

\section{Overview}
The Proof-of-Authority consensus algorithm~\cite{VWP18}, or POA in short, is efficient of using network bandwidth. It divides time into rounds with a fixed length and assumes that the majority of its (authorized) nodes perform consensus in the same round.

In each round, nodes select a leader (the node responsible for generating a new block) based on the round number, block height and their local views of active nodes. Therefore, the procedure can be considered instant, which allows more time for transmitting transaction (TX) data in each consensus round.

POA relies on its nodes to behave honestly based on their stake reputation and economic incentives. However, it cannot stop a malicious leader to produce two inconsistent blocks to cause forks or a collusion of consecutive leaders to produce a parallel chain.

To improve the security of POA, we propose to introduce a committee to endorse the block generated in each consensus round. The verifiable random function~(VRF)~\cite{PapEtAl99} is used for nodes to locally decide their committee memberships. With a committee, a malicious leader would have to collude with the committee to cause inconsistency. However, the property of VRF guarantees that the committee is selected randomly. Therefore, it makes it much more difficult for adversaries to launch such attacks.

\section{Specifications}
\subsection{Notations}
\renewcommand{\arraystretch}{2}
\begin{longtable}{p{3cm} p{10cm}}
    Symbol  & Description \\
    \hline\hline
    $N$ & Total number of nodes \\
    \hline
    $u=1,2,\dots,N$ & node index \\
    \hline
    $H(\cdot)$ & Cryptographic hash function \\
    \hline
    $\textrm{Sig}_u(\cdot)$ & Signature of $u$ \\
    \hline
    $\textrm{pk}_u$ & Public key of $u$ \\
    \hline
    $\textrm{sk}_u$ & Private key of $u$ \\
    \hline
    $\rho\left(\cdot\right)$ & Merkle root of the input set\\
    \hline\hline
    $r$ & Consensus round number \\
    \hline
    $l_r=1,2,...,N$ & Leader in round $r$ \\
    \hline
    $s_r$ & Block summary produced by $l_r$ \\
    \hline
    $\tau_r$ & $s_r\,\|\,\textrm{Sig}_{l_r}(s_r)$ \\
    \hline
    $d$ & Number of endorsements (from committee members) required for a valid block \\
    \hline
    $\Sigma_r$ & Pending transaction set prepared by $l_r$ \\
    \hline
    $B_{u,r}^*$ & Last block of the canonical chain recognized by $u$ in round $r$\\ 
    \hline
    $H_{vrf},\Pi_{vrf},V_{vrf}$ & Functions that compute hash, generate proof and verify proof defined in the VRF scheme, respectively \\
    \hline
    $\textrm{M}_r$ & Common VRF message generated for committee selection \\
    \hline
    $\omega$, $\omega^*$ & Branch and trunk \\
    \hline
    $m$, $L$ & Epoch number and the number of consensus rounds in one epoch \\
    \hline
    $b_m$ & Random beacon computed using randomness from the last block of the $m$'th epoch \\
    \hline
\end{longtable}

\subsection{Committee Membership}
\label{sec:committee}
The verifiable random function can be considered as a public-key version of keyed cryptographic hash. The hash of a given message can only be computed by the owner of the private key and can be verified by anyone given the public key and message. The scheme defines the following functions:
\begin{itemize}
    \item $\pi\leftarrow\Pi_{vrf}(\textrm{sk},m)$ - function that generates VRF proof;
    \item $\{T, F\}\leftarrow V_{vrf}(\textrm{pk}_u,m,\pi)$ - function that verify VRF proof;
    \item $h\leftarrow H_{vrf}(\textrm{sk},m)=H(\pi)$ - function that computes the hash.
\end{itemize}

Node~$u$ determines his committee membership by Algorithm~\ref{alg:committee-gen}. Here $\textrm{M}_r$ is the common VRF message computed in round $r$ and $\epsilon$ a predefined threshold. {\color{red} See Section~?? for details of the computation of $\theta_r$.}

\begin{algorithm}[H]
\caption{Procedure for $u$ to determine his committee membership. }
\label{alg:committee-gen}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    \State Compute $\pi_{u,r} = \Pi_{vrf}(\textrm{sk}_u,\textrm{M}_r)$ and $\lambda=H\left(\pi_{u,r}\right)$
    \If{$\lambda\leq\epsilon$}
        \State Return $\left(T,\pi_{u,r}\right)$
    \Else 
        \State Return $F$
    \EndIf
\end{algorithmic}
\end{spacing}
\end{algorithm}

\begin{algorithm}[H]
\caption{Procedure for anyone to validate $u$'s claimed committee membership.}
\label{alg:committee-valid}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    \If{$V_{vrf}(\textrm{pk}_u,\pi_{u,r})==F$}
        \State Return $F$
    \EndIf
    \State $\lambda\leftarrow H(\pi_{u,r})$
    \If{$\lambda\leq\epsilon$}
        \State Return $T$
    \Else 
        \State Return $F$
    \EndIf
\end{algorithmic}
\end{spacing}
\end{algorithm}

% The following is the procedure for node $u$ to decide whether he is a committee member in round $r$:
% \begin{enumerate}
%     \item Compute seed $\theta_r$. The computation is deterministic for all nodes;
%     \item Compute $\lambda=f_\textrm{vrf}\left(sk_u,\theta_r\right)$;
%     \item $u$ knows he is a committee member in round $r$ if $\lambda\leq\epsilon$ where $\epsilon$ is a predefined threshold.
% \end{enumerate}

\subsection{Block Summary}
Leader $l_r$ computes block summary~$s_r$ of the new block he wants to public and broadcast $s_r$ for endorsements from committee members. Algorithms~\ref{alg:bs-create} and \ref{alg:bs-valid} shows how to compute and validate $s_r$ for $l_r$ and other nodes, respectively.

\begin{algorithm}[H]
\caption{Procedure for $l_r$ to compute and broadcast $s_r$.}
\label{alg:bs-create}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    \State Prepares $\Sigma_r$ and computes $\rho\left(\Sigma_r\right)$
    \State Get the last block on the canonical chain, $B_{l_r}^*$ and computer $h_0=H(\textrm{Header}(B_{l_r,r}^*))$
    \State $s_r\leftarrow h_0\,\|\,r\,\|\,\rho\left(\Sigma_r\right)$
    \State Broadcast $\left(s_r,\textrm{Sig}_{l_r}(s_r)\right)$
\end{algorithmic}
\end{spacing}
\end{algorithm}

\begin{algorithm}[H]
\caption{Procedure for $u$ to validate $s_r$.}
\label{alg:bs-valid}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    \State Compute $l_r$
    \If{$s_r$ is not sent from $l_r$}
        \State Return $F$
    \EndIf
    \State Get $B_{u,r}^*$ and compute $\textrm{Header}(B_{u,r}^*)$
    \If{$\textrm{Header}(B_{u,r}^*)\neq\textrm{Header}(B_{l_r,r}^*)$}
        \State Return $F$
    \EndIf
    \State Verify $\textrm{Sig}_{l_r}(s_r)$
    \State Return $T$
\end{algorithmic}
\end{spacing}
\end{algorithm}

\subsection{Endorsement}

After receiving a block summary~$s_r$, if $u$ is a committee member, he then executes Algorithm~\ref{alg:endorse-gen} to endorse the block proposed by $l_r$. Here we define $\tau_r=s_r\,\|\,\textrm{Sig}_{l_r}(s_r)$.

\begin{algorithm}[H]
\caption{Procedure for $u$ to endorse a new block.}
\label{alg:endorse-gen}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    \State Verify $s_r$ by Algorithm~\ref{alg:bs-valid}
    \State Broadcast $\Big(u,s_r,\textrm{Sig}_u(\tau_r),\pi_{u,r}\Big)$
\end{algorithmic}
\end{spacing}
\end{algorithm}

Once a node receives an endorsement message from $u$, he first verify $s_r$ by Algorithm~\ref{alg:bs-valid} and then validate $u$'s endorsement by Algorithm~\ref{alg:endorse-valid}.

\begin{algorithm}[H]
\caption{Procedure for validating $u$'s endorsement.}
\label{alg:endorse-valid}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    % \If{$V_{vrf}(\textrm{pk}_u,\pi_{u,r})==FALSE$}
    %     \State Return $F$
    % \EndIf
    % \If{$H(\pi_{u,r})>\epsilon$}
    %     \State Return $F$
    % \EndIf
    \State Verify $u$'s committee membership by Algorithm~\ref{alg:committee-valid}
    \State Verify $\textrm{Sig}_{u}(\tau_r)$
\end{algorithmic}
\end{spacing}
\end{algorithm}

\subsection{Block}

Algorithm~\ref{alg:block-gen} describes the procedure for leader~$l_r$ to publish a new block in round~$r$.

\begin{algorithm}[H]
\caption{Procedure for $l_r$ to publish a new block.}
\label{alg:block-gen}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    \State Compute and broadcast $s_r$ by Algorithm~\ref{alg:bs-create}
    \State Broadcast $\Sigma_r$
    \State Wait for $d$ valid endorsements and arrange the committee members such that $u_1<u_2<\dots<u_d$
    \State $\Gamma_r\leftarrow\textrm{Sig}_{u_1}(\tau_r)\,\|\,\textrm{Sig}_{u_2}(\tau_r)\,\|\,\dots\,\|\,\textrm{Sig}_{u_d}(\tau_r)$
    \State Broadcast $\left(s_r,\textrm{Sig}_{l_r}(s_r),\textrm{Sig}_{l_r}(\Gamma_r),
    \left\{u_i,\textrm{Sig}_{u_i}(\tau_r),\pi_{u_i,r}\right\}_{i=1}^d\right)$
    \State Construct header body~$\Omega$ and broadcast $\textrm{Sig}_{l_r}(\Omega)$
\end{algorithmic}
\end{spacing}
\end{algorithm}

A block header body $\Omega$ contains the following elements:
\begin{enumerate}
    \item Hash of the parent header $H\left(\textrm{Header}\left(B_{l_r,r}^*\right)\right)$ 
    \item Round number $r$
    \item TX Merkle tree root $\rho\left(\Sigma_r\right)$
    \item Signature $\textrm{Sig}_{l_r}(s_r)$
    \item Committee member list $\left(u_1<u_2<\dots<u_d\right)$
    \item Merkle tree root of VRF proofs $\left\{\pi_{u_i,r}\right\}_{i=1}^d$
    \item Merkle tree root of signatures $\left\{\textrm{Sig}_{u_i}(\tau_r)\right\}_{i=1}^d$
    \item Signature $\textrm{Sig}_{l_r}(\Gamma_r)$
    % \item Other necessary header elements such as the state root, receipt root, gas limit and etc.
\end{enumerate}

A block consists of a header $\left\{\Omega,\textrm{Sig}_{l_r}(\Omega)\right\}$ and TX set~$\Sigma_r$.

\begin{algorithm}[H]
\caption{Procedure for validating a block.}
\label{alg:block-valid}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    \State Verify $s_r$ by Algorithm~\ref{alg:bs-valid}
    \For{$i=1,2,\dots,d$}
        \State Verify $u_i$'s endorsement by Algorithm~\ref{alg:endorse-valid}
    \EndFor
    \State Construct $\Gamma_r$ and verify $\textrm{Sig}_{l_r}(\Gamma_r)$
    \State Construct header body~$\Omega$ and verify $\textrm{Sig}_{l_r}(\Omega)$
    \State Verify $\Sigma_r$ and $\rho\left(\Sigma_r\right)$ 
\end{algorithmic}
\end{spacing}
\end{algorithm}

We only list the elements related to the committee mechanism for simplicity. Algorithms~\ref{alg:block-gen} and \ref{alg:block-valid} should be adjusted accordingly to accommodate other elements such as the gas limit, state root, receipt root, etc.

\subsection{Canonical Chain Rule}
Here we re-define the rules for selecting the canonical chain (or the \textit{trunk}) based on the committee mechanism.

Let $\omega$ be a branch, i.e., a chain of blocks. Given a block~$B$ on the branch, i.e.,~$B\in\omega$, we the weight of the chain starting from $B$ till the end of $\omega$,~$W(\omega,B)$, as the size of the set that contains all the leaders and committee members who have their signatures included in at least one block on the chain. Note that a node is counted as one no matter how many times he appears in the blocks.

Given two branches $\omega_1$ and $\omega_2$, let $B_0$ be the last block shared by $\omega_1$ and $\omega_2$, i.e., $B_0\in\omega_1\cap\,\omega_2$ and $\forall\, B'\in\omega_1\cap\,\omega_2,\, B'\preceq B_0$. Let $N(\omega,B)$ be the operator that finds the next block of $B$ on branch~$\omega$. We determine the canonical chain~$\omega^*$ from $\omega_1$ and $\omega_2$ by Algorithm~\ref{alg:canonical-chain}:

\begin{algorithm}[H]
\caption{Rules for choosing canonical chain~$\omega^*$ from branches~$\omega_1$ and $\omega_2$.}
\label{alg:canonical-chain}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    \State $B_1\leftarrow B_0$
    \State $B_2\leftarrow B_0$
    \While{$W(\omega_1,B_1)==W(\omega_2,B_2)$}
        \State $B_1\leftarrow N(\omega_1,B_1)$
        \State $B_2\leftarrow N(\omega_2,B_2)$
    \EndWhile
    \If{$W(\omega_1,B_1)>W(\omega_2,B_2)$}
        \State $\omega^*=\omega_1$
    \ElsIf{$W(\omega_1,B_1)<W(\omega_2,B_2)$}
        \State $\omega^*=\omega_2$
    \Else
        \If{$B_1$ is published later than $B_2$}
            \State $\omega^*=\omega_1$
        \Else
            \State $\omega^*=\omega_2$
        \EndIf
    \EndIf
\end{algorithmic}
\end{spacing}
\end{algorithm}

\subsection{Random Beacon}

As described in Section~\ref{sec:committee}, nodes need to compute a common message~$\textrm{M}_r$ to decide their committee memberships. It is desirable to add certain randomness in the computation such that adversaries only know their committee memberships in a limited period of time in future.

To do that, we divide the consensus process into epochs each of which lasts for $L$ consensus rounds where $L$ is a predetermined fixed number. Let $\hat{B}_m$ be the last block in the $m$'th epoch. We then define random beacon~$b_m$ as:

\begin{equation}
    b_m \leftarrow H(\textrm{Sig}_{l_{\hat{r}}}(\Gamma_{\hat{r}}))
\end{equation}

where $\hat{r}$ is the corresponding round number. We define $b_0=H(B_{\textrm{genesis}})$.

Beacon~$b_m$ can then be used to calculate VRF messages for the next $L$ rounds. In particular, we compute message~$\textrm{M}_r$ in round~$r$ as:

\begin{equation}
    \textrm{M}_r \leftarrow H(b_m\,\|\,r)
\end{equation}

where $mL+1\leq r\leq m(L+1)$.

It can be seen that even when the leader in round~$\hat{r}$ is malicious, the best he can do is to go through every combination of $d$ received valid endorsements and pick the one that maximizes his interest. In this way, we significantly limit the leader's influence on the beacon.

\subsection{Asynchronous Block Validation}

\subsection{Double-Spending Attack}
The main goal of introducing the committee mechanism is to make it much more difficult for malicious consensus nodes to cause inconsistency. The most damaging of such attacks is the double-spending attacks~(DSAs)~\cite{Sat08} where adversaries are allowed to take control of a few consecutive consensus rounds such that they can produce two parallel branches to launch an attack. Here we are going to infer a lower bound of the likelihood of launching a $k$-block DSA.

Let $p_\epsilon$ be the probability of a node being selected as a committee member. This probability is directly related to threshold value~$\epsilon$ and is equal to every node in every round due to the use of VRF. Assume that there are $f$ malicious nodes that can behave arbitrarily. To produce two valid, but contradicting blocks in the same round, adversaries must control both the leader and $d$ committee members. The probability of existence of $d$ committee members being malicious can be computed as:

\begin{equation}
    F(p_\epsilon,d,f) = \sum_{i=d}^f \binom{f}{i}\,{p_\epsilon}^i\left(1-p_\epsilon\right)^{f-i}
\end{equation}

Therefore, the probability of adversaries controlling the whole committee for $k$ consecutive rounds is $F(p_\epsilon,d,f)^k$. Table~\ref{tab:k-prob} lists the values of this probability with different inputs. We assign $f$ based on the Byzantine Fault Tolerance~(BFT) assumption which is considered reasonable and widely used in practice.

\begin{table}[H]
    \centering
    \begin{tabular}{|c|C{2.5cm}|C{2.5cm}|C{2.5cm}|}
        \hline
        $N=101$, $f=\lfloor\frac{N}{3}\rfloor$ & $k=1$ & $k=5$ & $k=10$ \\ 
        \hline\hline
        $p_\epsilon=0.1$, $d=7$ & $4.17\times10^{-2}$ & $1.26\times10^{-7}$ & $1.59\times10^{-14}$ \\
        \hline
        $p_\epsilon=0.1$, $d=8$ & $1.41\times10^{-2}$ & $5.58\times10^{-10}$ & $3.11\times10^{-19}$ \\
        \hline
        $p_\epsilon=0.15$, $d=11$ & $6.78\times10^{-3}$ & $1.43\times10^{-11}$ & $2.04\times10^{-22}$ \\
        \hline
    \end{tabular}
    \vspace{2ex}
    \caption{Probabilities $F(p_\epsilon,d,f)^k$ for different values of $p_\epsilon$, $d$ and $k$.}
    \label{tab:k-prob}
\end{table}

We consider the worse-case scenario when
\begin{enumerate}
    \item A malicious leader~$l_{\hat{r}}$ is selected to generate a block from which beacon~$b_m$ is computed;
    \item There are $k$ consecutive rounds in the $(m+1)$'th epoch where the leaders are all malicious.
\end{enumerate}
Let $c_{\hat{r}}$ be the total number of valid endorsements received by $l_{\hat{r}}$. The probability of launching a $k$-block DSA in the scenario can be computed as:

\begin{equation}
    F^*(k,p_\epsilon,d,f) = \binom{c_{\hat{r}}}{d}F(p_\epsilon,d,f)^k.
\end{equation}

In general, we can consider $F^*(k,p_\epsilon,d,f)$ as the lower bound of the probability of launching a $k$-block DSA.

% \Urlmuskip=0mu plus 1mu\relax
\bibliographystyle{unsrt}  
\bibliography{references}

\end{document}

### 2019-11-05 article.tex
1st proof-read

@@
 
-POA relies on its nodes to behave honestly based on their stake reputation and economic incentives.
-However, it cannot stop a malicious leader to produce two inconsistent blocks to cause forks or a collusion of consecutive leaders to produce a parallel chain.
-
-To improve the security of POA, we propose to introduce a committee to endorse the block generated in each consensus round.
+POA relies on the staked reputation (by nodes) and economic incentives to keep the system secure.
+However, it cannot stop malicious leaders causing temporary inconsistency.
+To improve the security of POA, we propose to introduce a committee to endorse the new block generated in each consensus round.
 The verifiable random function~(VRF)~\cite{PapEtAl99} is used for nodes to locally decide their committee memberships.
-With a committee, a malicious leader would have to collude with the committee to cause inconsistency.
+With the committee mechanism, a malicious leader would have to collude with the committee to cause inconsistency.
 However, the property of VRF guarantees that the committee is selected randomly.
@@
     \hline
-    $\textrm{Sig}_u(\cdot)$ & Signature of $u$ \\
+    ${\tt SIG}_u(\cdot)$ & Signature of $u$ \\
     \hline
-    $\textrm{pk}_u$ & Public key of $u$ \\
+    ${\tt PK}_u$ & Public key of $u$ \\
     \hline
-    $\textrm{sk}_u$ & Private key of $u$ \\
+    ${\tt SK}_u$ & Private key of $u$ \\
     \hline
     $\rho\left(\cdot\right)$ & Merkle root of the input set\\
-    \hline\hline
+    \hline
     $r$ & Consensus round number \\
@@
     \hline
-    $\tau_r$ & $s_r\,\|\,\textrm{Sig}_{l_r}(s_r)$ \\
+    $\tau_r$ & $s_r\,\|\,{\tt Sig}_{\,l_r}(s_r)$ \\
     \hline
-    $d$ & Number of endorsements (from committee members) required for a valid block \\
+    $\epsilon$ & Predefined threshold to determine committee memberships \\
+    \hline
+    $d$ & Number of endorsements required for forming a valid block \\
     \hline
@@
     \hline
-    $\textrm{M}_r$ & Common VRF message generated for committee selection \\
+    ${\tt M}_{\,r}$ & Common VRF message generated for committee selection \\
     \hline
@@
 The verifiable random function can be considered as a public-key version of keyed cryptographic hash.
-The hash of a given message can only be computed by the owner of the private key and can be verified by anyone given the public key and message.
+The hash of a given message can only be computed by the owner of the private key and can be verified by anyone given the public key~{\tt SK} and message~{\tt M}.
 The scheme defines the following functions:
 \begin{itemize}
-    \item $\pi\leftarrow\Pi_{vrf}(\textrm{sk},m)$ - function that generates VRF proof;
-    \item $\{T, F\}\leftarrow V_{vrf}(\textrm{pk}_u,m,\pi)$ - function that verify VRF proof;
-    \item $h\leftarrow H_{vrf}(\textrm{sk},m)=H(\pi)$ - function that computes the hash.
+    \item $\pi\leftarrow\Pi_{vrf}({\tt SK},{\tt M})$ - function that generates VRF proof;
+    \item $\{{\tt TRUE}, {\tt FALSE}\}\leftarrow V_{vrf}({\tt SK},{\tt M},\pi)$ - function that verify VRF proof;
+    \item $h\leftarrow H_{vrf}({\tt SK},{\tt M})=H(\pi)$ - function that computes the hash.
 \end{itemize}
@@
 Node~$u$ determines his committee membership by Algorithm~\ref{alg:committee-gen}.
-Here $\textrm{M}_r$ is the common VRF message computed in round $r$ and $\epsilon$ a predefined threshold.
-{\color{red} See Section~??
-for details of the computation of $\theta_r$.}
+Here ${\tt M}_{\,r}$ is the common VRF message computed in round $r$ and $\epsilon$ a predefined threshold.
+See Section~\ref{sec:beacon} for details of the computation of ${\tt M}_{\,r}$.
+Given the VRF proof and the corresponding public key, anyone can verify the membership claimed by $u$ by Algorithm~\ref{alg:endorse-valid} as shown below.
 
@@
     \vspace{1ex}
-    \State Compute $\pi_{u,r} = \Pi_{vrf}(\textrm{sk}_u,\textrm{M}_r)$ and $\lambda=H\left(\pi_{u,r}\right)$
+    \State Compute ${\tt M}_{\,r}$
+    \State Compute $\pi_{u,r} = \Pi_{vrf}({\tt SK}_u,{\tt M}_{\,r})$ and $\lambda=H\left(\pi_{u,r}\right)$
+    \vspace{1ex}
     \If{$\lambda\leq\epsilon$}
-        \State Return $\left(T,\pi_{u,r}\right)$
+        \State Return $\left({\tt TRUE},\pi_{u,r}\right)$
     \Else 
-        \State Return $F$
+        \State Return {\tt FALSE}
     \EndIf
@@
     \vspace{1ex}
-    \If{$V_{vrf}(\textrm{pk}_u,\pi_{u,r})==F$}
-        \State Return $F$
+    \State Compute ${\tt M}_{\,r}$
+    \vspace{1ex}
+    \If{$V_{vrf}({\tt PK}_u,\pi_{u,r})={\tt FALSE}$}
+        \State Return {\tt FALSE}
     \EndIf
+    \vspace{1ex}
     \State $\lambda\leftarrow H(\pi_{u,r})$
+    \vspace{1ex}
     \If{$\lambda\leq\epsilon$}
-        \State Return $T$
+        \State Return {\tt TRUE}
     \Else 
-        \State Return $F$
+        \State Return {\tt FALSE}
     \EndIf
@@
 
-% The following is the procedure for node $u$ to decide whether he is a committee member in round $r$:
-% \begin{enumerate}
-%     \item Compute seed $\theta_r$. The computation is deterministic for all nodes;
-%     \item Compute $\lambda=f_\textrm{vrf}\left(sk_u,\theta_r\right)$;
-%     \item $u$ knows he is a committee member in round $r$ if $\lambda\leq\epsilon$ where $\epsilon$ is a predefined threshold.
-% \end{enumerate}
-
 \subsection{Block Summary}
-Leader $l_r$ computes block summary~$s_r$ of the new block he wants to public and broadcast $s_r$ for endorsements from committee members.
-Algorithms~\ref{alg:bs-create} and \ref{alg:bs-valid} shows how to compute and validate $s_r$ for $l_r$ and other nodes, respectively.
+At the beginning of round~$r$, leader $l_r$ computes the summary of the new block, $s_r$, and broadcast it for the committee members to endorse the block.
+Algorithms~\ref{alg:bs-gen} and \ref{alg:bs-valid} shows the computation and validation process of $s_r$, respectively.
+In Algorithm~\ref{alg:bs-valid}, $B_{u,r}^*$ is the last block of the canonical chain locally recognized by $u$ at the beginning of round~$r$.
+Lines~6-10 dictate that $l_r$'s view on the canonical chain must be consistent with that of $u$.
 
@@
 \caption{Procedure for $l_r$ to compute and broadcast $s_r$.}
-\label{alg:bs-create}
+\label{alg:bs-gen}
 \begin{spacing}{1.2}
@@
     \State Prepares $\Sigma_r$ and computes $\rho\left(\Sigma_r\right)$
-    \State Get the last block on the canonical chain, $B_{l_r}^*$ and computer $h_0=H(\textrm{Header}(B_{l_r,r}^*))$
+    \State Get the last block on the canonical chain, $B_{l_r}^*$ and computer $h_0=H({\tt HEADER}(B_{l_r,r}^*))$
     \State $s_r\leftarrow h_0\,\|\,r\,\|\,\rho\left(\Sigma_r\right)$
-    \State Broadcast $\left(s_r,\textrm{Sig}_{l_r}(s_r)\right)$
+    \State Broadcast $\left(s_r,{\tt Sig}_{\,l_r}(s_r)\right)$
 \end{algorithmic}
@@
     \If{$s_r$ is not sent from $l_r$}
-        \State Return $F$
+        \State Return {\tt FALSE}
     \EndIf
-    \State Get $B_{u,r}^*$ and compute $\textrm{Header}(B_{u,r}^*)$
-    \If{$\textrm{Header}(B_{u,r}^*)\neq\textrm{Header}(B_{l_r,r}^*)$}
-        \State Return $F$
+    \vspace{1ex}
+    \State Verify ${\tt Sig}_{\,l_r}(s_r)$
+    \vspace{1ex}
+    \State Extract $B_{u,r}^*$ and compute ${\tt HEADER}(B_{u,r}^*)$
+    \If{${\tt HEADER}(B_{u,r}^*)\neq{\tt HEADER}(B_{l_r,r}^*)$}
+        \State Return {\tt FALSE}
     \EndIf
-    \State Verify $\textrm{Sig}_{l_r}(s_r)$
-    \State Return $T$
+    \vspace{1ex}
+    \State Return {\tt TRUE}
 \end{algorithmic}
@@
 
-After receiving a block summary~$s_r$, if $u$ is a committee member, he then executes Algorithm~\ref{alg:endorse-gen} to endorse the block proposed by $l_r$.
-Here we define $\tau_r=s_r\,\|\,\textrm{Sig}_{l_r}(s_r)$.
+After receiving block summary~$s_r$, if node~$u$ is a committee member, he then executes Algorithm~\ref{alg:endorse-gen} to endorse the block proposed by $l_r$.
+Here we define $\tau_r=s_r\,\|\,{\tt Sig}_{\,l_r}(s_r)$.
 
@@
     \State Verify $s_r$ by Algorithm~\ref{alg:bs-valid}
-    \State Broadcast $\Big(u,s_r,\textrm{Sig}_u(\tau_r),\pi_{u,r}\Big)$
+    \State Broadcast $\Big(u,s_r,{\tt SIG}_u(\tau_r),\pi_{u,r}\Big)$
 \end{algorithmic}
@@
     \vspace{1ex}
-    % \If{$V_{vrf}(\textrm{pk}_u,\pi_{u,r})==FALSE$}
-    %     \State Return $F$
-    % \EndIf
-    % \If{$H(\pi_{u,r})>\epsilon$}
-    %     \State Return $F$
-    % \EndIf
+    \State Verify ${\tt SIG}_{u}(\tau_r)$
     \State Verify $u$'s committee membership by Algorithm~\ref{alg:committee-valid}
-    \State Verify $\textrm{Sig}_{u}(\tau_r)$
 \end{algorithmic}
@@
     \vspace{1ex}
-    \State Compute and broadcast $s_r$ by Algorithm~\ref{alg:bs-create}
-    \State Broadcast $\Sigma_r$
+    \State Compute and broadcast $s_r$ by Algorithm~\ref{alg:bs-gen}
+    \State Broadcast TX set~$\Sigma_r$
     \State Wait for $d$ valid endorsements and arrange the committee members such that $u_1<u_2<\dots<u_d$
-    \State $\Gamma_r\leftarrow\textrm{Sig}_{u_1}(\tau_r)\,\|\,\textrm{Sig}_{u_2}(\tau_r)\,\|\,\dots\,\|\,\textrm{Sig}_{u_d}(\tau_r)$
-    \State Broadcast $\left(s_r,\textrm{Sig}_{l_r}(s_r),\textrm{Sig}_{l_r}(\Gamma_r),
-    \left\{u_i,\textrm{Sig}_{u_i}(\tau_r),\pi_{u_i,r}\right\}_{i=1}^d\right)$
-    \State Construct header body~$\Omega$ and broadcast $\textrm{Sig}_{l_r}(\Omega)$
+    \State $\Gamma_r\leftarrow{\tt SIG}_{u_1}(\tau_r)\,\|\,{\tt SIG}_{u_2}(\tau_r)\,\|\,\dots\,\|\,{\tt SIG}_{u_d}(\tau_r)$
+    \State Broadcast $\left(s_r,{\tt Sig}_{\,l_r}(s_r),{\tt Sig}_{\,l_r}(\Gamma_r),
+    \left\{u_i,{\tt SIG}_{u_i}(\tau_r),\pi_{u_i,r}\right\}_{i=1}^d\right)$
+    \State Construct header body~$\Omega$ and broadcast ${\tt Sig}_{\,l_r}(\Omega)$
 \end{algorithmic}
@@
 \begin{enumerate}
-    \item Hash of the parent header $H\left(\textrm{Header}\left(B_{l_r,r}^*\right)\right)$ 
+    \item Hash of the parent header $H({\tt HEADER}(B_{l_r,r}^*))$ 
     \item Round number $r$
     \item TX Merkle tree root $\rho\left(\Sigma_r\right)$
-    \item Signature $\textrm{Sig}_{l_r}(s_r)$
+    \item Signature ${\tt Sig}_{\,l_r}(s_r)$
     \item Committee member list $\left(u_1<u_2<\dots<u_d\right)$
     \item Merkle tree root of VRF proofs $\left\{\pi_{u_i,r}\right\}_{i=1}^d$
-    \item Merkle tree root of signatures $\left\{\textrm{Sig}_{u_i}(\tau_r)\right\}_{i=1}^d$
-    \item Signature $\textrm{Sig}_{l_r}(\Gamma_r)$
+    \item Merkle tree root of signatures $\left\{{\tt SIG}_{u_i}(\tau_r)\right\}_{i=1}^d$
+    \item Signature ${\tt Sig}_{\,l_r}(\Gamma_r)$
     % \item Other necessary header elements such as the state root, receipt root, gas limit and etc.
@@
 
-A block consists of a header $\left\{\Omega,\textrm{Sig}_{l_r}(\Omega)\right\}$ and TX set~$\Sigma_r$.
+A block consists of a header $\left\{\Omega,{\tt Sig}_{\,l_r}(\Omega)\right\}$ and TX set~$\Sigma_r$.
 
@@
     \State Verify $s_r$ by Algorithm~\ref{alg:bs-valid}
+    \State Verify $\rho\left(\Sigma_r\right)$
     \For{$i=1,2,\dots,d$}
@@
     \EndFor
-    \State Construct $\Gamma_r$ and verify $\textrm{Sig}_{l_r}(\Gamma_r)$
-    \State Construct header body~$\Omega$ and verify $\textrm{Sig}_{l_r}(\Omega)$
-    \State Verify $\Sigma_r$ and $\rho\left(\Sigma_r\right)$ 
+    \State Construct $\Gamma_r$ and verify ${\tt Sig}_{\,l_r}(\Gamma_r)$
+    \State Construct header body~$\Omega$ and verify ${\tt Sig}_{\,l_r}(\Omega)$
+    \State Verify $\Sigma_r$ 
 \end{algorithmic}
@@
 
-We only list the elements related to the committee mechanism for simplicity.
+Note that we only list the elements related to the committee mechanism for simplicity.
 Algorithms~\ref{alg:block-gen} and \ref{alg:block-valid} should be adjusted accordingly to accommodate other elements such as the gas limit, state root, receipt root, etc.
@@
 \subsection{Canonical Chain Rule}
-Here we re-define the rules for selecting the canonical chain (or the \textit{trunk}) based on the committee mechanism.
-
+In this subsection, we provide the rules for selecting the canonical chain (or the \textit{trunk}) based on the committee mechanism.
 Let $\omega$ be a branch, i.e., a chain of blocks.
-Given a block~$B$ on the branch, i.e.,~$B\in\omega$, we the weight of the chain starting from $B$ till the end of $\omega$,~$W(\omega,B)$, as the size of the set that contains all the leaders and committee members who have their signatures included in at least one block on the chain.
-Note that a node is counted as one no matter how many times he appears in the blocks.
+Given a block~$B$ on the branch, i.e.,~$B\in\omega$, we define the weight of the chain starting from $B$ till the end of $\omega$,~$W(\omega,B)$, as the size of the set that contains all the leaders and committee members who have their signatures included in at least one block on the chain.
+Note that a node is only counted once.
 
@@
 Let $N(\omega,B)$ be the operator that finds the next block of $B$ on branch~$\omega$.
-We determine the canonical chain~$\omega^*$ from $\omega_1$ and $\omega_2$ by Algorithm~\ref{alg:canonical-chain}:
+We choose the canonical chain~$\omega^*$ from two branches~$\omega_1$ and $\omega_2$ by Algorithm~\ref{alg:canonical-chain} as shown below:
 
@@
     \vspace{1ex}
-    \State $B_1\leftarrow B_0$
-    \State $B_2\leftarrow B_0$
-    \While{$W(\omega_1,B_1)==W(\omega_2,B_2)$}
+    \State $B_1\leftarrow N(\omega_1,B_0)$
+    \State $B_2\leftarrow N(\omega_2,B_0)$
+    \vspace{1ex}
+    \While{$W(\omega_1,B_1)=W(\omega_2,B_2)$ \textbf{and} $N(\omega_1,B_1)\neq{\tt nil}$ \textbf{and} $N(\omega_2,B_2)\neq{\tt nil}$}
         \State $B_1\leftarrow N(\omega_1,B_1)$
@@
     \EndWhile
+    \vspace{1ex}
     \If{$W(\omega_1,B_1)>W(\omega_2,B_2)$}
-        \State $\omega^*=\omega_1$
+        \State $\omega^*\leftarrow\omega_1$
     \ElsIf{$W(\omega_1,B_1)<W(\omega_2,B_2)$}
-        \State $\omega^*=\omega_2$
+        \State $\omega^*\leftarrow\omega_2$
     \Else
         \If{$B_1$ is published later than $B_2$}
-            \State $\omega^*=\omega_1$
+            \State $\omega^*\leftarrow\omega_1$
         \Else
-            \State $\omega^*=\omega_2$
+            \State $\omega^*\leftarrow\omega_2$
         \EndIf
@@
 \subsection{Random Beacon}
+\label{sec:beacon}
 
-As described in Section~\ref{sec:committee}, nodes need to compute a common message~$\textrm{M}_r$ to decide their committee memberships.
-It is desirable to add certain randomness in the computation such that adversaries only know their committee memberships in a limited period of time in future.
+In Algorithms~\ref{alg:committee-gen} and \ref{alg:committee-valid}, nodes need to compute common message~${\tt M}_{\,r}$ to determine and validate committee memberships.
+It is desirable to add certain randomness in the computation such that adversaries only know their committee memberships in a limited number of rounds in future.
 
-To do that, we divide the consensus process into epochs each of which lasts for $L$ consensus rounds where $L$ is a predetermined fixed number.
-Let $\hat{B}_m$ be the last block in the $m$'th epoch.
-We then define random beacon~$b_m$ as:
+To do that, we divide the consensus process into epochs each of which lasts for $L$ rounds where $L$ is a predetermined fixed number.
+Let $\hat{B}_{u,r}^{\,m}$ be the last block on the canonical chain observed by $u$ in the $m$'th epoch.
+Node~$u$ can compute a random beacon~$b_u^m$ from $\hat{B}_{u,r}^{\,m}$ as:
 
 \begin{equation}
-    b_m \leftarrow H(\textrm{Sig}_{l_{\hat{r}}}(\Gamma_{\hat{r}}))
+    b_u^m \leftarrow H({\tt Sig}_{\,l_r}(\Gamma_{r})).
 \end{equation}
 
-where $\hat{r}$ is the corresponding round number. We define $b_0=H(B_{\textrm{genesis}})$.
+Here we define $b_u^0=H(B_{\textrm{genesis}})$.
 
-Beacon~$b_m$ can then be used to calculate VRF messages for the next $L$ rounds. In particular, we compute message~$\textrm{M}_r$ in round~$r$ as:
+Beacon~$b_u^m$ is then used to calculate VRF messages for the next epoch. In particular, we compute message~${\tt M}_{\,r'}$ in round~$r'$ as:
 
 \begin{equation}
-    \textrm{M}_r \leftarrow H(b_m\,\|\,r)
+    {\tt M}_{\,r'} \leftarrow H(b_u^m\,\|\,r')
 \end{equation}
 
-where $mL+1\leq r\leq m(L+1)$.
+where $mL+1\leq r'\leq m(L+1)$.
 
-It can be seen that even when the leader in round~$\hat{r}$ is malicious, the best he can do is to go through every combination of $d$ received valid endorsements and pick the one that maximizes his interest.
-In this way, we significantly limit the leader's influence on the beacon.
+Now let us consider the case when the leader who generates $\hat{B}_{u,r}^{\,m}$ is malicious.
+Since signatures from the committee members are deterministic, the best he can do is to go through every combination of $d$ signatures and pick the one that maximizes his interest.
+The number of possible trials is fairly limited and therefore, we significantly limit the leader's influence on the beacon.
 
-\subsection{Asynchronous Block Validation}
+\subsection{Optimizing Bandwidth Usage}
+A more efficient usage of network bandwidth often results in a higher system throughput.
+By more efficient, we mean that there is more time to transmit TXs in each round of consensus.
+To do that, we detach the endorsing process from the block validation process.
+In particular, committee members can endorse a new block without receiving and validating the complete set of TXs included in the block.
+See Algorithms~\ref{alg:bs-gen} and \ref{alg:bs-valid} for details.
+In this way, we would be able to significantly shorten the whole endorsing process and potentially allow more bandwidth used for TX transmission.
+
+Note that TXs will be checked by nodes when validating any newly received block and any invalid TX will cause the block to be discarded even though all the endorsements are valid.
+
+\subsection{Block Reward}
+With the committee mechanism in place, the block reward needs to be shared between the leader and committee members.
+We propose to give half of the total block reward to the leader and the rest equally distributed to the committee members.
 
 \subsection{Double-Spending Attack}
-The main goal of introducing the committee mechanism is to make it much more difficult for malicious consensus nodes to cause inconsistency.
-The most damaging of such attacks is the double-spending attacks~(DSAs)~\cite{Sat08} where adversaries are allowed to take control of a few consecutive consensus rounds such that they can produce two parallel branches to launch an attack.
-Here we are going to infer a lower bound of the likelihood of launching a $k$-block DSA.
+The main goal of introducing the committee mechanism is to make it more difficult for adversaries to cause inconsistency.
+Perhaps the most damaging of such attacks is the double-spending attacks~(DSAs)~\cite{Sat08} where adversaries are allowed to take control of a few consecutive consensus rounds such that they can produce two parallel branches to launch a DSA.
+Here we are going to infer a lower bound for the probability of launching a $k$-block DSA.
 
 Let $p_\epsilon$ be the probability of a node being selected as a committee member.
-This probability is directly related to threshold value~$\epsilon$ and is equal to every node in every round due to the use of VRF.
-Assume that there are $f$ malicious nodes that can behave arbitrarily.
+This probability is directly related to threshold~$\epsilon$ and is equal to every node thanks to VRF.
+Let us assume that there are $f$ malicious nodes that can behave arbitrarily.
 To produce two valid, but contradicting blocks in the same round, adversaries must control both the leader and $d$ committee members.
@@
 
-Therefore, the probability of adversaries controlling the whole committee for $k$ consecutive rounds is $F(p_\epsilon,d,f)^k$.
+Therefore, the probability of adversaries controlling the committee for $k$ consecutive rounds is $F(p_\epsilon,d,f)^k$.
 Table~\ref{tab:k-prob} lists the values of this probability with different inputs.
-We assign $f$ based on the Byzantine Fault Tolerance~(BFT) assumption which is considered reasonable and widely used in practice.
+We set $f$ according to the Byzantine Fault Tolerance~(BFT) assumption.
+It is a security assumptioned that is considered reasonable and widely used in practice.
 
@@
 
-We consider the worse-case scenario when
+Now let us consider the worse-case scenario when
 \begin{enumerate}
-    \item A malicious leader~$l_{\hat{r}}$ is selected to generate a block from which beacon~$b_m$ is computed;
-    \item There are $k$ consecutive rounds in the $(m+1)$'th epoch where the leaders are all malicious.
+    \item A malicious leader is selected to generate the block in the last epoch from which the random beacon for the current epoch is computed;
+    \item There are $k$ consecutive rounds in the current epoch where the leaders are all malicious.
 \end{enumerate}
-Let $c_{\hat{r}}$ be the total number of valid endorsements received by $l_{\hat{r}}$. The probability of launching a $k$-block DSA in the scenario can be computed as:
+Let $c$ be the total number of valid endorsements received by the leader mentioned in the first condition. The probability of launching a $k$-block DSA in the scenario can be computed as:
 
 \begin{equation}
-    F^*(k,p_\epsilon,d,f) = \binom{c_{\hat{r}}}{d}F(p_\epsilon,d,f)^k.
+    F^*(k,p_\epsilon,d,f) = \binom{c}{d}\,F(p_\epsilon,d,f)^k.
 \end{equation}
 
-In general, we can consider $F^*(k,p_\epsilon,d,f)$ as the lower bound of the probability of launching a $k$-block DSA.
+In general, we can consider $F^*(k,p_\epsilon,d,f)$ as the lower bound for the probability of launching a $k$-block DSA.
 

### 2019-11-07 article.tex
Added VIP header
Remove vip header from tex

@@
 \usepackage{amsmath}
+\usepackage{multirow}
 
@@
 }
-\date{}
+
+\date{\vspace{-5ex}}
 
@@
 
+\usepackage{abstract}
+\renewcommand{\abstractname}{}
+\renewcommand{\absnamepos}{empty}
+
 \begin{document}
@@
 % \begin{abstract}
+% \begin{itemize}
+%     \item VIP: 193
+%     \item Title: Committee-Based POA
+%     \item Author: Ziheng Zhou (peter.zhou@vechain.com) and Zhijie Ren (zhijie.ren@vechain.com)
+%     \item Category: Core
+%     \item Status: Draft
+%     \item CreateAt: 2019-11-05
+% \end{itemize}
 % \end{abstract}
@@
 We set $f$ according to the Byzantine Fault Tolerance~(BFT) assumption.
-It is a security assumptioned that is considered reasonable and widely used in practice.
+It is a security assumption that is considered reasonable and widely used in practice.
+
+Now let us consider the worse-case scenario when a malicious leader is selected to generate the block in the last epoch from which the random beacon for the current epoch is computed.
+The best he can do is to try all the combinations of $d$ valid signatures he receives from the committee members to search for a combination that will result in $k$ consecutive rounds in which leaders are all malicious in the next epoch.
+Therefore, we can compute a lower bound for the probability of launching a $k$-block DSA as:
+
+\begin{equation}
+    F^*(k,p_\epsilon,d,f) = \binom{c}{d}\cdot\left(\frac{f}{N}\right)^k\cdot F(p_\epsilon,d,f)^k.
+\end{equation}
+
+where $c$ is the total number of committee-member signatures the leader receives. Table~\ref{tab:dsa-prob} below provides some example of the probabilities of launching a DSA.
 
@@
     \centering
-    \begin{tabular}{|c|C{2.5cm}|C{2.5cm}|C{2.5cm}|}
+    \begin{tabular}{|c|C{2.5cm}|C{2.5cm}|}
         \hline
-        $N=101$, $f=\lfloor\frac{N}{3}\rfloor$ & $k=1$ & $k=5$ & $k=10$ \\ 
+        $N = 101$, $f=33$ & $k=5$ & $k=10$ \\
         \hline\hline
-        $p_\epsilon=0.1$, $d=7$ & $4.17\times10^{-2}$ & $1.26\times10^{-7}$ & $1.59\times10^{-14}$ \\
+        $d=5$ & $1.57\times10^{-6}$ & $4.38\times10^{-14}$ \\
         \hline
-        $p_\epsilon=0.1$, $d=8$ & $1.41\times10^{-2}$ & $5.58\times10^{-10}$ & $3.11\times10^{-19}$ \\
-        \hline
-        $p_\epsilon=0.15$, $d=11$ & $6.78\times10^{-3}$ & $1.43\times10^{-11}$ & $2.04\times10^{-22}$ \\
+        $d=10$ & $6.04\times10^{-8}$ & $4.56\times10^{-19}$ \\
         \hline
@@
     \vspace{2ex}
-    \caption{Probabilities $F(p_\epsilon,d,f)^k$ for different values of $p_\epsilon$, $d$ and $k$.}
-    \label{tab:k-prob}
+    \caption{Examples of probabilities $F(p_\epsilon,d,f)^k$. Here we compute $p_\epsilon=1.5\cdot d/N$ and $c=\lfloor1.5\cdot d\rfloor$.}
+    \label{tab:dsa-prob}
 \end{table}
-
-Now let us consider the worse-case scenario when
-\begin{enumerate}
-    \item A malicious leader is selected to generate the block in the last epoch from which the random beacon for the current epoch is computed;
-    \item There are $k$ consecutive rounds in the current epoch where the leaders are all malicious.
-\end{enumerate}
-Let $c$ be the total number of valid endorsements received by the leader mentioned in the first condition. The probability of launching a $k$-block DSA in the scenario can be computed as:
-
-\begin{equation}
-    F^*(k,p_\epsilon,d,f) = \binom{c}{d}\,F(p_\epsilon,d,f)^k.
-\end{equation}
-
-In general, we can consider $F^*(k,p_\epsilon,d,f)$ as the lower bound for the probability of launching a $k$-block DSA.
 

### 2019-11-07 article.tex
fix ref

@@
 A block consists of a header $\left\{\Omega,{\tt Sig}_{\,l_r}(\Omega)\right\}$ and TX set~$\Sigma_r$.
+Algorithm~\ref{alg:block-valid} describes how to validate a block generated in round $r$.
+To prevent a malicious leader to deliberately delay the transmission of block elements to cause inconsistency, honest nodes would accept a new block only if they validated it in the same round.
 
 \begin{algorithm}[H]
-\caption{Procedure for validating a block.}
+\caption{Procedure for validating a block generated in round $r$.}
 \label{alg:block-valid}
@@
 Here we are going to infer a lower bound for the probability of launching a $k$-block DSA.
+We focus on solving the DSA in a practical synchronous network setting, where we assume that a message be broadcast through the gossip protocol and reach the whole network with some bounded delay.
 
@@
 Therefore, the probability of adversaries controlling the committee for $k$ consecutive rounds is $F(p_\epsilon,d,f)^k$.
-Table~\ref{tab:k-prob} lists the values of this probability with different inputs.
+Table~\ref{tab:dsa-prob} lists the values of this probability with different inputs.
 We set $f$ according to the Byzantine Fault Tolerance~(BFT) assumption.

### 2019-11-08 dsa-prob.ts
code for computing Table 2

@@ -1,0 +1,25 @@
+import * as math from 'mathjs';
+
+function F(p: number, d: number, f: number): number {
+    let r = 0;
+    for (let i = d; i <= f; i++) {
+        r = r + math.combinations(f, i) * Math.pow(p, i) * Math.pow(1 - p, f - i);
+    }
+    return r;
+}
+
+const f = 33;
+const N = 101;
+const ds = [5, 10];
+const ps = ds.map(x => x / 101 * 1.5);
+const ks = [5, 10];
+for (let i in ds) {
+    const d = ds[i];
+    const p = ps[i];
+    console.log('> ' + F(p, d, f).toExponential(2));
+    for (let j in ks) {
+        const k = ks[j];
+        console.log('* ' + Math.pow(F(p, d, f), k).toExponential(2));
+        console.log('# ' + (Math.pow(F(p, d, f), k) * Math.pow(f / N, k) * math.combinations(Math.ceil(N * p), d)).toExponential(2));
+    }
+}

### 2019-11-12 article.tex
add assumptions

@@
 It divides time into rounds with a fixed length and assumes that the majority of its (authorized) nodes perform consensus in the same round.
-
 In each round, nodes select a leader (the node responsible for generating a new block) based on the round number, block height and their local views of active nodes.
@@
 
+We assume that the network is synchronous and the messages are transmitted through gossip communication, i.e., if an honest node sends a message or an honest node receives a message, all other honest nodes will receive same message within at most a delay of $\tau$, which is determined by the network configuration and known in advance.
+
+%Note that besides the network synchrony, we also assume that messages be transmitted through gossip communication.
+Hence, if an honest node receives a message, all other honest nodes will receive the same message with a bounded delay.
 \section{Specifications}
@@
 Here we are going to infer a lower bound for the probability of launching a $k$-block DSA.
-We focus on solving the DSA in a practical synchronous network setting, where we assume that a message be broadcast through the gossip protocol and reach the whole network with some bounded delay.
 
@@
 
-where $c$ is the total number of committee-member signatures the leader receives. Table~\ref{tab:dsa-prob} below provides some example of the probabilities of launching a DSA.
+where $c$ is the total number of committee-member signatures the leader receives. Table~\ref{tab:dsa-prob} below provides some examples of the probabilities of launching a DSA.
 

### 2019-11-21 article.tex
fix num

@@
 Perhaps the most damaging of such attacks is the double-spending attacks~(DSAs)~\cite{Sat08} where adversaries are allowed to take control of a few consecutive consensus rounds such that they can produce two parallel branches to launch a DSA.
-Here we are going to infer a lower bound for the probability of launching a $k$-block DSA.
+Here we are going to infer a upper bound for the probability of launching a $k$-block DSA.
 
@@
 The best he can do is to try all the combinations of $d$ valid signatures he receives from the committee members to search for a combination that will result in $k$ consecutive rounds in which leaders are all malicious in the next epoch.
-Therefore, we can compute a lower bound for the probability of launching a $k$-block DSA as:
+Therefore, we can compute a upper bound for the probability of launching a $k$-block DSA as:
 
@@
         \hline\hline
-        $d=5$ & $1.57\times10^{-6}$ & $4.38\times10^{-14}$ \\
+        $d=5$ & $1.86\times10^{-7}$ & $1.65\times10^{-15}$ \\
         \hline
-        $d=10$ & $6.04\times10^{-8}$ & $4.56\times10^{-19}$ \\
+        $d=10$ & $2.78\times10^{-8}$ & $1.17\times10^{-19}$ \\
         \hline

### 2019-11-27 article.tex

@@
 \begin{equation}
-    b_u^m \leftarrow H({\tt Sig}_{\,l_r}(\Gamma_{r})).
+    b_u^m \leftarrow H({\tt Sig}_{\,l_r}(\pi_{u_1,r}\,\|\,\pi_{u_1,r}\,\|\,\cdots\,\|\,\pi_{u_d,r})).
 \end{equation}
 
-Here we define $b_u^0=H(B_{\textrm{genesis}})$.
-
-Beacon~$b_u^m$ is then used to calculate VRF messages for the next epoch. In particular, we compute message~${\tt M}_{\,r'}$ in round~$r'$ as:
+Here we define $b_u^0\leftarrow H(B_{\textrm{genesis}})$. Beacon~$b_u^m$ is then used to calculate VRF messages for the next epoch. In particular, we compute message~${\tt M}_{\,r'}$ in round~$r'$ as:
 
@@
 Now let us consider the case when the leader who generates $\hat{B}_{u,r}^{\,m}$ is malicious.
-Since signatures from the committee members are deterministic, the best he can do is to go through every combination of $d$ signatures and pick the one that maximizes his interest.
+Since signatures from the committee members are deterministic, the best he can do is to go through every combination of $d$ signatures from all the signatures he has received from committee members and pick the one that maximizes his interest.
 The number of possible trials is fairly limited and therefore, we significantly limit the leader's influence on the beacon.

### 2020-02-27 article.tex
ongoing final verison

@@
 \section{Overview}
-The Proof-of-Authority consensus algorithm~\cite{VWP18}, or POA in short, is efficient of using network bandwidth.
+The Proof-of-Authority consensus algorithm~\cite{VWP18}, or PoA in short, is efficient of using network bandwidth.
 It divides time into rounds with a fixed length and assumes that the majority of its (authorized) nodes perform consensus in the same round.
-In each round, nodes select a leader (the node responsible for generating a new block) based on the round number, block height and their local views of active nodes.
+In each round, nodes select a leader (the node responsible for generating a new block) based on the round number, block height and their local views of the active nodes.
 Therefore, the procedure can be considered instant, which allows more time for transmitting transaction (TX) data in each consensus round.
 
-POA relies on the staked reputation (by nodes) and economic incentives to keep the system secure.
-However, it cannot stop malicious leaders causing temporary inconsistency.
-To improve the security of POA, we propose to introduce a committee to endorse the new block generated in each consensus round.
-The verifiable random function~(VRF)~\cite{PapEtAl99} is used for nodes to locally decide their committee memberships.
-With the committee mechanism, a malicious leader would have to collude with the committee to cause inconsistency.
+However, PoA cannot prevent a malicious leader from causing temporary inconsistency by producing multiple blocks.
+To improve the security of PoA, we propose to introduce a committee (a group of selected nodes) to endorse the new block generated in each consensus round.
+The verifiable random function~(VRF)~\cite{PapEtAl99} is used for committee selection in each round.
+With the committee mechanism, a malicious leader would have to collude with committee members to cause inconsistency.
 However, the property of VRF guarantees that the committee is selected randomly.
@@
 
-We assume that the network is synchronous and the messages are transmitted through gossip communication, i.e., if an honest node sends a message or an honest node receives a message, all other honest nodes will receive same message within at most a delay of $\tau$, which is determined by the network configuration and known in advance.
+It is assumed that the network is synchronous and the messages are transmitted through gossip communication, i.e., if an honest node sends a message or an honest node receives a message, all other honest nodes will receive same message within at most a delay of $\tau$, which is determined by the network configuration and is known in advance.
 
@@
     \hline
-    ${\tt PK}_u$ & Public key of $u$ \\
-    \hline
-    ${\tt SK}_u$ & Private key of $u$ \\
+    $\left({\tt PK}_u,{\tt SK}_u\right)$ & Public and private keys generated by $u$ to sign blocks \\
     \hline
@@
     \hline
-    $\epsilon$ & Predefined threshold to determine committee memberships \\
+    $\epsilon$ & Predefined threshold to determine committee membership \\
     \hline
-    $d$ & Number of endorsements required for forming a valid block \\
+    $d$ & Number of endorsements required to produce a valid block \\
     \hline
-    $\Sigma_r$ & Pending transaction set prepared by $l_r$ \\
+    $\Sigma_r$ & Transaction set prepared by $l_r$ \\
     \hline
-    $B_{u,r}^*$ & Last block of the canonical chain recognized by $u$ in round $r$\\ 
+    $B_{u,r}^*$ & Last block of the canonical chain (trunk) recognized by $u$ in round $r$\\ 
     \hline
@@
     \hline
+    $\left({\tt PK}_u^{vrf},{\tt SK}_u^{vrf}\right)$ & Public and private key pair generated by $u$ for VRF  \\
+    \hline
     ${\tt M}_{\,r}$ & Common VRF message generated for committee selection \\
     \hline
-    $\omega$, $\omega^*$ & Branch and trunk \\
-    \hline
+    % $\omega$, $\omega^*$ & Branch and trunk \\
+    % \hline
     $m$, $L$ & Epoch number and the number of consensus rounds in one epoch \\
@@
 \label{sec:committee}
-The verifiable random function can be considered as a public-key version of keyed cryptographic hash.
+The verifiable random function can be considered a public-key version of keyed cryptographic hash.
 The hash of a given message can only be computed by the owner of the private key and can be verified by anyone given the public key~{\tt SK} and message~{\tt M}.
@@
 Node~$u$ determines his committee membership by Algorithm~\ref{alg:committee-gen}.
-Here ${\tt M}_{\,r}$ is the common VRF message computed in round $r$ and $\epsilon$ a predefined threshold.
-See Section~\ref{sec:beacon} for details of the computation of ${\tt M}_{\,r}$.
-Given the VRF proof and the corresponding public key, anyone can verify the membership claimed by $u$ by Algorithm~\ref{alg:endorse-valid} as shown below.
+Here ${\tt M}_{\,r}$ can be locally computed by each node in a deterministic way and $\epsilon$ a predefined threshold.
+See Section~\ref{sec:beacon} for details of how to compute ${\tt M}_{\,r}$.
+Given the VRF proof~$\pi_{u,r}$ and the corresponding public key~${\tt PK}_u^{vrf}$, anyone can verify the membership claimed by $u$ by Algorithm~\ref{alg:committee-valid} below.
 
@@
     \State Compute ${\tt M}_{\,r}$
-    \State Compute $\pi_{u,r} = \Pi_{vrf}({\tt SK}_u,{\tt M}_{\,r})$ and $\lambda=H\left(\pi_{u,r}\right)$
+    \State Compute $\pi_{u,r} = \Pi_{vrf}({\tt SK}_u^{vrf},{\tt M}_{\,r})$ and $\lambda=H\left(\pi_{u,r}\right)$
     \vspace{1ex}
@@
     \vspace{1ex}
-    \If{$V_{vrf}({\tt PK}_u,\pi_{u,r})={\tt FALSE}$}
+    \If{$V_{vrf}({\tt PK}_u^{vrf},\pi_{u,r})={\tt FALSE}$}
         \State Return {\tt FALSE}
@@
 
-\subsection{Canonical Chain Rule}
-In this subsection, we provide the rules for selecting the canonical chain (or the \textit{trunk}) based on the committee mechanism.
+% \subsection{Canonical Chain Rule}
+% In this subsection, we provide the rules for selecting the canonical chain (or the \textit{trunk}) based on the committee mechanism.
 Let $\omega$ be a branch, i.e., a chain of blocks.
@@
 
-Given two branches $\omega_1$ and $\omega_2$, let $B_0$ be the last block shared by $\omega_1$ and $\omega_2$, i.e., $B_0\in\omega_1\cap\,\omega_2$ and $\forall\, B'\in\omega_1\cap\,\omega_2,\, B'\preceq B_0$.
+% Given two branches $\omega_1$ and $\omega_2$, let $B_0$ be the last block shared by $\omega_1$ and $\omega_2$, i.e., $B_0\in\omega_1\cap\,\omega_2$ and $\forall\, B'\in\omega_1\cap\,\omega_2,\, B'\preceq B_0$.
 Let $N(\omega,B)$ be the operator that finds the next block of $B$ on branch~$\omega$.
@@
 
-\begin{algorithm}[H]
-\caption{Rules for choosing canonical chain~$\omega^*$ from branches~$\omega_1$ and $\omega_2$.}
-\label{alg:canonical-chain}
-\begin{spacing}{1.2}
-\begin{algorithmic}[1]
-    \vspace{1ex}
-    \State $B_1\leftarrow N(\omega_1,B_0)$
-    \State $B_2\leftarrow N(\omega_2,B_0)$
-    \vspace{1ex}
-    \While{$W(\omega_1,B_1)=W(\omega_2,B_2)$ \textbf{and} $N(\omega_1,B_1)\neq{\tt nil}$ \textbf{and} $N(\omega_2,B_2)\neq{\tt nil}$}
-        \State $B_1\leftarrow N(\omega_1,B_1)$
-        \State $B_2\leftarrow N(\omega_2,B_2)$
-    \EndWhile
-    \vspace{1ex}
-    \If{$W(\omega_1,B_1)>W(\omega_2,B_2)$}
-        \State $\omega^*\leftarrow\omega_1$
-    \ElsIf{$W(\omega_1,B_1)<W(\omega_2,B_2)$}
-        \State $\omega^*\leftarrow\omega_2$
-    \Else
-        \If{$B_1$ is published later than $B_2$}
-            \State $\omega^*\leftarrow\omega_1$
-        \Else
-            \State $\omega^*\leftarrow\omega_2$
-        \EndIf
-    \EndIf
-\end{algorithmic}
-\end{spacing}
-\end{algorithm}
+% \begin{algorithm}[H]
+% \caption{Rules for choosing canonical chain~$\omega^*$ from branches~$\omega_1$ and $\omega_2$.}
+% \label{alg:canonical-chain}
+% \begin{spacing}{1.2}
+% \begin{algorithmic}[1]
+%     \vspace{1ex}
+%     \State $B_1\leftarrow N(\omega_1,B_0)$
+%     \State $B_2\leftarrow N(\omega_2,B_0)$
+%     \vspace{1ex}
+%     \While{$W(\omega_1,B_1)=W(\omega_2,B_2)$ \textbf{and} $N(\omega_1,B_1)\neq{\tt nil}$ \textbf{and} $N(\omega_2,B_2)\neq{\tt nil}$}
+%         \State $B_1\leftarrow N(\omega_1,B_1)$
+%         \State $B_2\leftarrow N(\omega_2,B_2)$
+%     \EndWhile
+%     \vspace{1ex}
+%     \If{$W(\omega_1,B_1)>W(\omega_2,B_2)$}
+%         \State $\omega^*\leftarrow\omega_1$
+%     \ElsIf{$W(\omega_1,B_1)<W(\omega_2,B_2)$}
+%         \State $\omega^*\leftarrow\omega_2$
+%     \Else
+%         \If{$B_1$ is published later than $B_2$}
+%             \State $\omega^*\leftarrow\omega_1$
+%         \Else
+%             \State $\omega^*\leftarrow\omega_2$
+%         \EndIf
+%     \EndIf
+% \end{algorithmic}
+% \end{spacing}
+% \end{algorithm}
 

### 2020-02-28 article.tex
revision after my vip193 implemetation

@@
     \hline
-    $\left({\tt PK}_u,{\tt SK}_u\right)$ & Public and private keys generated by $u$ to sign blocks \\
-    \hline
+    % $\left({\tt PK}_u,{\tt SK}_u\right)$ & Public and private keys generated by $u$ to sign blocks \\
+    % \hline
     $\rho\left(\cdot\right)$ & Merkle root of the input set\\
@@
     \hline
+    $\Sigma_r$ & Transaction set prepared by $l_r$ \\
+    \hline
     $s_r$ & Block summary produced by $l_r$ \\
     \hline
-    $\tau_r$ & $s_r\,\|\,{\tt Sig}_{\,l_r}(s_r)$ \\
+    $x_r$ & Tx-set package produced by $l_r$ \\
     \hline
-    $\epsilon$ & Predefined threshold to determine committee membership \\
+    $e_{u,r}$ & Endorsement produced by $u$ \\
     \hline
@@
     \hline
-    $\Sigma_r$ & Transaction set prepared by $l_r$ \\
+    $\pi_{u,r}$ & VRF proof produced by $u$ \\
     \hline
-    $B_{u,r}^*$ & Last block of the canonical chain (trunk) recognized by $u$ in round $r$\\ 
+    $h_r$ & Block header produced by $l_r$ \\
     \hline
-    $H_{vrf},\Pi_{vrf},V_{vrf}$ & Functions that compute hash, generate proof and verify proof defined in the VRF scheme, respectively \\
-    \hline
-    $\left({\tt PK}_u^{vrf},{\tt SK}_u^{vrf}\right)$ & Public and private key pair generated by $u$ for VRF  \\
-    \hline
-    ${\tt M}_{\,r}$ & Common VRF message generated for committee selection \\
-    \hline
-    % $\omega$, $\omega^*$ & Branch and trunk \\
+    % $\tau_r$ & $s_r\,\|\,{\tt Sig}_{\,l_r}(s_r)$ \\
     % \hline
-    $m$, $L$ & Epoch number and the number of consensus rounds in one epoch \\
-    \hline
-    $b_m$ & Random beacon computed using randomness from the last block of the $m$'th epoch \\
-    \hline
+    % $\epsilon$ & Predefined threshold to determine committee membership \\
+    % \hline
+    % $B_{u,r}^*$ & Last block of the canonical chain (trunk) recognized by $u$ in round $r$\\ 
+    % \hline
+    % $H_{vrf},\Pi_{vrf},V_{vrf}$ & Functions that compute hash, generate proof and verify proof defined in the VRF scheme, respectively \\
+    % \hline
+    % $\left({\tt PK}_u^{vrf},{\tt SK}_u^{vrf}\right)$ & Public and private key pair generated by $u$ for VRF  \\
+    % \hline
+    % ${\tt M}_{\,r}$ & Common VRF message generated for committee selection \\
+    % \hline
+    % % $\omega$, $\omega^*$ & Branch and trunk \\
+    % % \hline
+    % $m$, $L$ & Epoch number and the number of consensus rounds in one epoch \\
+    % \hline
+    % $b_m$ & Random beacon computed using randomness from the last block of the $m$'th epoch \\
+    % \hline
 \end{longtable}
 
-\subsection{Committee Membership}
-\label{sec:committee}
-The verifiable random function can be considered a public-key version of keyed cryptographic hash.
-The hash of a given message can only be computed by the owner of the private key and can be verified by anyone given the public key~{\tt SK} and message~{\tt M}.
-The scheme defines the following functions:
+\subsection{Producing a New Block}
+
+Algorithm~\ref{alg:block-gen} describes the procedure for leader~$l_r$ to publish a new block in round~$r$. During the process, nodes needs to deal with four types of packages: 
 \begin{itemize}
-    \item $\pi\leftarrow\Pi_{vrf}({\tt SK},{\tt M})$ - function that generates VRF proof;
-    \item $\{{\tt TRUE}, {\tt FALSE}\}\leftarrow V_{vrf}({\tt SK},{\tt M},\pi)$ - function that verify VRF proof;
-    \item $h\leftarrow H_{vrf}({\tt SK},{\tt M})=H(\pi)$ - function that computes the hash.
+    \item Block summary~$s_r$
+    \item Tx-set package~$x_r$
+    \item Endorsement~$e_{u,r}$
+    \item Block header~$h_r$
 \end{itemize}
-
-Node~$u$ determines his committee membership by Algorithm~\ref{alg:committee-gen}.
-Here ${\tt M}_{\,r}$ can be locally computed by each node in a deterministic way and $\epsilon$ a predefined threshold.
-See Section~\ref{sec:beacon} for details of how to compute ${\tt M}_{\,r}$.
-Given the VRF proof~$\pi_{u,r}$ and the corresponding public key~${\tt PK}_u^{vrf}$, anyone can verify the membership claimed by $u$ by Algorithm~\ref{alg:committee-valid} below.
+They will be described in detail in later sections.
 
 \begin{algorithm}[H]
-\caption{Procedure for $u$ to determine his committee membership. }
-\label{alg:committee-gen}
+\caption{Procedure for $l_r$ to publish a new block.}
+\label{alg:block-gen}
 \begin{spacing}{1.2}
@@
     \vspace{1ex}
-    \State Compute ${\tt M}_{\,r}$
-    \State Compute $\pi_{u,r} = \Pi_{vrf}({\tt SK}_u^{vrf},{\tt M}_{\,r})$ and $\lambda=H\left(\pi_{u,r}\right)$
-    \vspace{1ex}
-    \If{$\lambda\leq\epsilon$}
-        \State Return $\left({\tt TRUE},\pi_{u,r}\right)$
-    \Else 
-        \State Return {\tt FALSE}
-    \EndIf
-\end{algorithmic}
-\end{spacing}
-\end{algorithm}
-
-\begin{algorithm}[H]
-\caption{Procedure for anyone to validate $u$'s claimed committee membership.}
-\label{alg:committee-valid}
-\begin{spacing}{1.2}
-\begin{algorithmic}[1]
-    \vspace{1ex}
-    \State Compute ${\tt M}_{\,r}$
-    \vspace{1ex}
-    \If{$V_{vrf}({\tt PK}_u^{vrf},\pi_{u,r})={\tt FALSE}$}
-        \State Return {\tt FALSE}
-    \EndIf
-    \vspace{1ex}
-    \State $\lambda\leftarrow H(\pi_{u,r})$
-    \vspace{1ex}
-    \If{$\lambda\leq\epsilon$}
-        \State Return {\tt TRUE}
-    \Else 
-        \State Return {\tt FALSE}
-    \EndIf
+    \State Prepare and broadcast $s_r$
+    \State Prepare and broadcast $x_r$ if there is any tx included in the new block
+    \State Wait for $d$ valid endorsements 
+    %and arrange the committee members such that ${\tt PK}_{u_1}^{vrf}<{\tt PK}_{u_2}^{vrf}<\dots<{\tt PK}_{u_d}^{vrf}$
+    % \State $\Gamma_r\leftarrow{\tt SIG}_{u_1}(\tau_r)\,\|\,{\tt SIG}_{u_2}(\tau_r)\,\|\,\dots\,\|\,{\tt SIG}_{u_d}(\tau_r)$
+    % \State Broadcast $\left(s_r,{\tt Sig}_{\,l_r}(s_r),{\tt Sig}_{\,l_r}(\Gamma_r),
+    % \left\{{\tt SIG}_{u_i}(\tau_r),\pi_{u_i,r}\right\}_{i=1}^d\right)$
+    % \State Construct header body~$\Omega$ and broadcast ${\tt Sig}_{\,l_r}(\Omega)$
+    \State Prepare and broadcast $h_r$
 \end{algorithmic}
@@
 \subsection{Block Summary}
-At the beginning of round~$r$, leader $l_r$ computes the summary of the new block, $s_r$, and broadcast it for the committee members to endorse the block.
-Algorithms~\ref{alg:bs-gen} and \ref{alg:bs-valid} shows the computation and validation process of $s_r$, respectively.
-In Algorithm~\ref{alg:bs-valid}, $B_{u,r}^*$ is the last block of the canonical chain locally recognized by $u$ at the beginning of round~$r$.
-Lines~6-10 dictate that $l_r$'s view on the canonical chain must be consistent with that of $u$.
+At the beginning of round~$r$, leader $l_r$ computes a summary of the proposed new block, $s_r$, and broadcast it for the committee members to endorse.
+A block summary must include the following information:
+\begin{itemize}
+    \item Parent header reference
+    \item Merkle root of the transactions included in the new block, $\rho(\Sigma_r)$
+    \item Round number, $r$
+    \item Leader's signature, ${\tt SIG}_{\,l_r}(\bar{s}_r)$ where $\bar{s}_r$ represents the block summary without a signature
+\end{itemize}
 
-\begin{algorithm}[H]
-\caption{Procedure for $l_r$ to compute and broadcast $s_r$.}
-\label{alg:bs-gen}
-\begin{spacing}{1.2}
-\begin{algorithmic}[1]
-    \vspace{1ex}
-    \State Prepares $\Sigma_r$ and computes $\rho\left(\Sigma_r\right)$
-    \State Get the last block on the canonical chain, $B_{l_r}^*$ and computer $h_0=H({\tt HEADER}(B_{l_r,r}^*))$
-    \State $s_r\leftarrow h_0\,\|\,r\,\|\,\rho\left(\Sigma_r\right)$
-    \State Broadcast $\left(s_r,{\tt Sig}_{\,l_r}(s_r)\right)$
-\end{algorithmic}
-\end{spacing}
-\end{algorithm}
+% Algorithms~\ref{alg:bs-gen} and \ref{alg:bs-valid} shows the computation and validation processes of $s_r$, respectively.
+
+% \begin{algorithm}[H]
+% \caption{Procedure for $l_r$ to compute and broadcast $s_r$.}
+% \label{alg:bs-gen}
+% \begin{spacing}{1.2}
+% \begin{algorithmic}[1]
+%     \vspace{1ex}
+%     \State Prepares $\Sigma_r$ and computes $\rho\left(\Sigma_r\right)$
+%     \State Get $B_{l_r}^*$
+%     % \State Get the last block on the canonical chain, $B_{l_r}^*$ and computer $h_0=H({\tt HEADER}(B_{l_r,r}^*))$
+%     % \State $s_r\leftarrow h_0\,\|\,r\,\|\,\rho\left(\Sigma_r\right)$
+%     \State Prepare $s_r$
+%     \State Broadcast $\left(s_r,{\tt Sig}_{\,l_r}(s_r)\right)$
+% \end{algorithmic}
+% \end{spacing}
+% \end{algorithm}
+
+Algorithm~\ref{alg:bs-valid} shows how to validate an incoming block summary.
 
@@
     \vspace{1ex}
-    \State Compute $l_r$
-    \If{$s_r$ is not sent from $l_r$}
-        \State Return {\tt FALSE}
-    \EndIf
+    \State Verify ${\tt Sig}_{\,l_r}(\bar{s}_r)$
+    \State Verify that $r$ is the current round
+    \State Verify that $l_r$ is the round leader
+    \State Verify that the parent block referred by $s_r$ is consistent with the latest block on the canonical chain
+\end{algorithmic}
+\end{spacing}
+\end{algorithm}
+
+\subsection{Tx-Set Package}
+After broadcasting $s_r$, leader~$l_r$ needs to prepare and broadcast the tx-set package~$x_r$. A tx-set package must include the following information:
+\begin{itemize}
+    \item Round number, $r$
+    \item Set of txs included in the new block, $\Sigma_r$
+    \item Leader's signature, ${\tt SIG}_{\,l_r}(\bar{x}_r)$ where $\bar{x}_r$ represents the tx-set package without a signature
+\end{itemize}
+
+Algorithm~\ref{alg:txset-valid} shows how to validate an incoming tx-set package.
+
+\begin{algorithm}[H]
+\caption{Procedure for validating $x_r$.}
+\label{alg:txset-valid}
+\begin{spacing}{1.2}
+\begin{algorithmic}[1]
     \vspace{1ex}
-    \State Verify ${\tt Sig}_{\,l_r}(s_r)$
-    \vspace{1ex}
-    \State Extract $B_{u,r}^*$ and compute ${\tt HEADER}(B_{u,r}^*)$
-    \If{${\tt HEADER}(B_{u,r}^*)\neq{\tt HEADER}(B_{l_r,r}^*)$}
-        \State Return {\tt FALSE}
-    \EndIf
-    \vspace{1ex}
-    \State Return {\tt TRUE}
+    \State Verify ${\tt SIG}_{\,l_r}(\bar{x}_r)$
+    \State Verify that $r$ is the current round
+    \State Verify that $l_r$ is the round leader
 \end{algorithmic}
@@
 
-After receiving block summary~$s_r$, if node~$u$ is a committee member, he then executes Algorithm~\ref{alg:endorse-gen} to endorse the block proposed by $l_r$.
-Here we define $\tau_r=s_r\,\|\,{\tt Sig}_{\,l_r}(s_r)$.
+After receiving and verifying $s_r$, nodes~$u$ that are selected as the committee members need to prepare and broadcast endorsements~$e_{u,r}$.
+An endorsement~$e_{u,r}$ must include the following information:
+\begin{itemize}
+    \item Received and verified block summary, $b_r$
+    \item VRF proof of $u$'s committee membership, $\pi_{u,r}$
+    \item Signature, ${\tt SIG}_{\,l_r}(\bar{e}_{u,r})$ where $\bar{e}_{u,r}$ represents the endorsement without a signature
+\end{itemize}
 
-\begin{algorithm}[H]
-\caption{Procedure for $u$ to endorse a new block.}
-\label{alg:endorse-gen}
-\begin{spacing}{1.2}
-\begin{algorithmic}[1]
-    \vspace{1ex}
-    \State Verify $s_r$ by Algorithm~\ref{alg:bs-valid}
-    \State Broadcast $\Big(u,s_r,{\tt SIG}_u(\tau_r),\pi_{u,r}\Big)$
-\end{algorithmic}
-\end{spacing}
-\end{algorithm}
+{\color{red} Note that it is assumed that the private key used by $u$ to generate $\pi_{u,r}$ is different from the one that generates $u$'s address.
+It is also assumed that the corresponding public key that will be used by other nodes to verify VRF proof can be assessed so that it does not needs to be transmitted with $e_{u,r}$.}
 
-Once a node receives an endorsement message from $u$, he first verify $s_r$ by Algorithm~\ref{alg:bs-valid} and then validate $u$'s endorsement by Algorithm~\ref{alg:endorse-valid}.
+% Here we define $\tau_r=s_r\,\|\,{\tt Sig}_{\,l_r}(s_r)$.
+% \begin{algorithm}[H]
+% \caption{Procedure for $u$ to endorse a new block.}
+% \label{alg:endorse-gen}
+% \begin{spacing}{1.2}
+% \begin{algorithmic}[1]
+%     \vspace{1ex}
+%     \State Verify $s_r$ by Algorithm~\ref{alg:bs-valid}
+%     \State Broadcast $\Big(u,s_r,{\tt SIG}_u(\tau_r),\pi_{u,r}\Big)$
+% \end{algorithmic}
+% \end{spacing}
+% \end{algorithm}
+
+Algorithm~\ref{alg:endorse-valid} shows how to validate an incoming endorsement by $u$.
 
@@
     \State Verify ${\tt SIG}_{u}(\tau_r)$
+    \State Verify $s_r$ by Algorithm~\ref{alg:bs-valid}
     \State Verify $u$'s committee membership by Algorithm~\ref{alg:committee-valid}
@@
 
-\subsection{Block}
+\subsection{Block Header}
 
-Algorithm~\ref{alg:block-gen} describes the procedure for leader~$l_r$ to publish a new block in round~$r$.
+After receiving $d$ valid endorsements, leader~$l_r$ needs to prepare and broadcast the header of the new block. A block header~$h_r$ must contain the following information:
+\begin{itemize}
+    \item Parent header reference 
+    \item Round number, $r$
+    \item Merkle tree root of the tx set, $\rho\left(\Sigma_r\right)$
+    \item Leader's signature on the block summary, ${\tt Sig}_{\,l_r}(s_r)$
+    \item VRF proofs of the committee membership from $d$ nodes, $\left\{\pi_{u_i,r}\right\}_{i=1}^d$
+    \item Endorsement signatures from the same $d$ nodes, $\left\{{\tt SIG}_{u_i}(\bar{e}_{u,r})\right\}_{i=1}^d$
+    \item For any $1\leq i<j\leq N$, $u_i$'s public key for verifying $\pi_{u_i,r}$ should be strictly smaller than that of $u_j$
+    \item Leader's signature, ${\tt Sig}_{\,l_r}(\bar{h}_r)$ where $\bar{h}_r$ represents the header without a signature
+    % \item Committee member list $\left(u_1<u_2<\dots<u_d\right)$
+    % \item Merkle tree root of VRF proofs $\left\{\pi_{u_i,r}\right\}_{i=1}^d$
+    % \item Merkle tree root of signatures $\left\{{\tt SIG}_{u_i}(\tau_r)\right\}_{i=1}^d$
+    % \item Signature ${\tt Sig}_{\,l_r}(\Gamma_r)$
+    % \item Other necessary header elements such as the state root, receipt root, gas limit and etc.
+\end{itemize}
+
+% A block consists of a header $\left\{\Omega,{\tt Sig}_{\,l_r}(\Omega)\right\}$ and tx set~$\Sigma_r$. 
+Algorithm~\ref{alg:header-valid} describes how to validate a block header generated in round $r$.
+
+%To prevent a malicious leader to deliberately delay the transmission of block elements to cause inconsistency, honest nodes would accept a new block only if they validated it in the same round.
 
 \begin{algorithm}[H]
-\caption{Procedure for $l_r$ to publish a new block.}
-\label{alg:block-gen}
+\caption{Procedure for validating the header of the new block generated in round $r$.}
+\label{alg:header-valid}
 \begin{spacing}{1.2}
@@
     \vspace{1ex}
-    \State Compute and broadcast $s_r$ by Algorithm~\ref{alg:bs-gen}
-    \State Broadcast TX set~$\Sigma_r$
-    \State Wait for $d$ valid endorsements and arrange the committee members such that $u_1<u_2<\dots<u_d$
-    \State $\Gamma_r\leftarrow{\tt SIG}_{u_1}(\tau_r)\,\|\,{\tt SIG}_{u_2}(\tau_r)\,\|\,\dots\,\|\,{\tt SIG}_{u_d}(\tau_r)$
-    \State Broadcast $\left(s_r,{\tt Sig}_{\,l_r}(s_r),{\tt Sig}_{\,l_r}(\Gamma_r),
-    \left\{u_i,{\tt SIG}_{u_i}(\tau_r),\pi_{u_i,r}\right\}_{i=1}^d\right)$
-    \State Construct header body~$\Omega$ and broadcast ${\tt Sig}_{\,l_r}(\Omega)$
+    \State Verify ${\tt Sig}_{\,l_r}(\bar{h}_r)$
+    \State Verify that $r$ is the current round
+    \State Verify that $l_r$ is the round leader
+    \State Reconstruct and verify $s_r$ by Algorithm~\ref{alg:bs-valid}
+    % \State Verify $\rho\left(\Sigma_r\right)$
+    \For{$i=1,2,\dots,d$}
+        \If{$i>1$}
+            \State Verify that $u_i$'s public key for verifying $\pi_{u_i,r}$ is larger than that of $u_{i-1}$
+        \EndIf
+        \State Reconstruct and Verify $e_{u_i,r}$ by Algorithm~\ref{alg:endorse-valid}
+    \EndFor
+    % \State Construct $\Gamma_r$ and verify ${\tt Sig}_{\,l_r}(\Gamma_r)$
+    % \State Construct header body~$\Omega$ and verify ${\tt Sig}_{\,l_r}(\Omega)$
+    % \State Verify $\Sigma_r$ 
 \end{algorithmic}
@@
 
-A block header body $\Omega$ contains the following elements:
-\begin{enumerate}
-    \item Hash of the parent header $H({\tt HEADER}(B_{l_r,r}^*))$ 
-    \item Round number $r$
-    \item TX Merkle tree root $\rho\left(\Sigma_r\right)$
-    \item Signature ${\tt Sig}_{\,l_r}(s_r)$
-    \item Committee member list $\left(u_1<u_2<\dots<u_d\right)$
-    \item Merkle tree root of VRF proofs $\left\{\pi_{u_i,r}\right\}_{i=1}^d$
-    \item Merkle tree root of signatures $\left\{{\tt SIG}_{u_i}(\tau_r)\right\}_{i=1}^d$
-    \item Signature ${\tt Sig}_{\,l_r}(\Gamma_r)$
-    % \item Other necessary header elements such as the state root, receipt root, gas limit and etc.
-\end{enumerate}
-
-A block consists of a header $\left\{\Omega,{\tt Sig}_{\,l_r}(\Omega)\right\}$ and TX set~$\Sigma_r$.
-Algorithm~\ref{alg:block-valid} describes how to validate a block generated in round $r$.
-To prevent a malicious leader to deliberately delay the transmission of block elements to cause inconsistency, honest nodes would accept a new block only if they validated it in the same round.
+\subsection{Block Assembling}
+To use the network bandwidth more efficient, the round leader does not broadcast the whole block, but broadcast the tx-set~$x_r$ and block header~$h_r$ asynchronously.
+Other nodes need to assemble the new block locally following Algorithm~\ref{alg:block-assembling}.
 
 \begin{algorithm}[H]
-\caption{Procedure for validating a block generated in round $r$.}
-\label{alg:block-valid}
+\caption{Procedure for verify and assemble the new block generated in round $r$.}
+\label{alg:block-assembling}
 \begin{spacing}{1.2}
@@
     \vspace{1ex}
-    \State Verify $s_r$ by Algorithm~\ref{alg:bs-valid}
-    \State Verify $\rho\left(\Sigma_r\right)$
-    \For{$i=1,2,\dots,d$}
-        \State Verify $u_i$'s endorsement by Algorithm~\ref{alg:endorse-valid}
-    \EndFor
-    \State Construct $\Gamma_r$ and verify ${\tt Sig}_{\,l_r}(\Gamma_r)$
-    \State Construct header body~$\Omega$ and verify ${\tt Sig}_{\,l_r}(\Omega)$
-    \State Verify $\Sigma_r$ 
+    \State Verify $h_r$ by Algorithm~\ref{alg:header-valid}
+    \State Verify $x_r$ by Algorithm~\ref{alg:txset-valid}
+    \State Verify that $\rho(\Sigma_r)$ in $h_r$ is consistent with $x_r$
+    \State Verify txs included in $x_r$
+    \State Assemble the new block
 \end{algorithmic}
@@
 \end{algorithm}
-
-Note that we only list the elements related to the committee mechanism for simplicity.
-Algorithms~\ref{alg:block-gen} and \ref{alg:block-valid} should be adjusted accordingly to accommodate other elements such as the gas limit, state root, receipt root, etc.
 
@@
 
+\subsection{Committee Membership}
+\label{sec:committee}
+The verifiable random function can be considered a public-key version of keyed cryptographic hash.
+The hash of a given message can only be computed by the owner of the private key~${\tt SK}$ and can be verified by anyone given the public key~{\tt SK} and message~{\tt M}.
+The scheme defines the following functions:
+\begin{itemize}
+    \item $\pi\leftarrow\Pi_{vrf}({\tt SK},{\tt M})$ - function that generates VRF proof;
+    \item $\{{\tt TRUE}, {\tt FALSE}\}\leftarrow V_{vrf}({\tt SK},{\tt M},\pi)$ - function that verify VRF proof;
+    \item $h\leftarrow H_{vrf}({\tt SK},{\tt M})=H(\pi)$ - function that computes the hash.
+\end{itemize}
+
+Node~$u$ determines his committee membership using his private key~${\tt SK}_u$ by Algorithm~\ref{alg:committee-gen}.
+Here ${\tt M}_{\,r}$ can be locally computed by each node in a deterministic way and $\epsilon$ a predefined threshold.
+See Section~\ref{sec:beacon} for details of how to compute ${\tt M}_{\,r}$.
+Given the VRF proof~$\pi_{u,r}$ and the corresponding public key~${\tt PK}_u$, anyone can verify the membership claimed by $u$ by Algorithm~\ref{alg:committee-valid} below.
+
+\begin{algorithm}[H]
+\caption{Procedure for $u$ to determine his committee membership. }
+\label{alg:committee-gen}
+\begin{spacing}{1.2}
+\begin{algorithmic}[1]
+    \vspace{1ex}
+    \State Compute ${\tt M}_{\,r}$
+    \State Compute $\pi_{u,r} = \Pi_{vrf}({\tt SK}_u,{\tt M}_{\,r})$ and $\lambda=H\left(\pi_{u,r}\right)$
+    \vspace{1ex}
+    \If{$\lambda\leq\epsilon$}
+        \State Return $\left({\tt TRUE},\pi_{u,r}\right)$
+    \Else 
+        \State Return {\tt FALSE}
+    \EndIf
+\end{algorithmic}
+\end{spacing}
+\end{algorithm}
+
+\begin{algorithm}[H]
+\caption{Procedure for anyone to validate $u$'s claimed committee membership.}
+\label{alg:committee-valid}
+\begin{spacing}{1.2}
+\begin{algorithmic}[1]
+    \vspace{1ex}
+    \State Compute ${\tt M}_{\,r}$
+    \vspace{1ex}
+    \If{$V_{vrf}({\tt PK}_u,\pi_{u,r})={\tt FALSE}$}
+        \State Return {\tt FALSE}
+    \EndIf
+    \vspace{1ex}
+    \State $\lambda\leftarrow H(\pi_{u,r})$
+    \vspace{1ex}
+    \If{$\lambda\leq\epsilon$}
+        \State Return {\tt TRUE}
+    \Else 
+        \State Return {\tt FALSE}
+    \EndIf
+\end{algorithmic}
+\end{spacing}
+\end{algorithm}
+
 \subsection{Random Beacon}
@@
 
-In Algorithms~\ref{alg:committee-gen} and \ref{alg:committee-valid}, nodes need to compute common message~${\tt M}_{\,r}$ to determine and validate committee memberships.
+Nodes need to compute common message~${\tt M}_{\,r}$ to determine and validate committee memberships.
 It is desirable to add certain randomness in the computation such that adversaries only know their committee memberships in a limited number of rounds in future.
@@
 
-\subsection{Optimizing Bandwidth Usage}
-A more efficient usage of network bandwidth often results in a higher system throughput.
-By more efficient, we mean that there is more time to transmit TXs in each round of consensus.
-To do that, we detach the endorsing process from the block validation process.
-In particular, committee members can endorse a new block without receiving and validating the complete set of TXs included in the block.
-See Algorithms~\ref{alg:bs-gen} and \ref{alg:bs-valid} for details.
-In this way, we would be able to significantly shorten the whole endorsing process and potentially allow more bandwidth used for TX transmission.
-
-Note that TXs will be checked by nodes when validating any newly received block and any invalid TX will cause the block to be discarded even though all the endorsements are valid.
-
-\subsection{Block Reward}
-With the committee mechanism in place, the block reward needs to be shared between the leader and committee members.
+% \subsection{Block Reward}
+% With the committee mechanism in place, the block reward needs to be shared between the leader and committee members.
 We propose to give half of the total block reward to the leader and the rest equally distributed to the committee members.

### 2020-03-03 article.tex

@@
     \item Endorsement signatures from the same $d$ nodes, $\left\{{\tt SIG}_{u_i}(\bar{e}_{u,r})\right\}_{i=1}^d$
-    \item For any $1\leq i<j\leq N$, $u_i$'s public key for verifying $\pi_{u_i,r}$ should be strictly smaller than that of $u_j$
+    \item $\forall\,1\leq i<j\leq N$, $\pi_{u_i,r}<\pi_{u,j}$. It is made to reduce the number of combinations $l_r$ can try when arranging the vrf proofs.
     \item Leader's signature, ${\tt Sig}_{\,l_r}(\bar{h}_r)$ where $\bar{h}_r$ represents the header without a signature
@@
         \If{$i>1$}
-            \State Verify that $u_i$'s public key for verifying $\pi_{u_i,r}$ is larger than that of $u_{i-1}$
+            \State Verify that $\pi_{u,i-1} < \pi_{u,i}$
         \EndIf

### 2020-03-09 article.tex

@@
 {\color{red} Note that it is assumed that the private key used by $u$ to generate $\pi_{u,r}$ is different from the one that generates $u$'s address.
-It is also assumed that the corresponding public key that will be used by other nodes to verify VRF proof can be assessed so that it does not needs to be transmitted with $e_{u,r}$.}
+It is also assumed that the corresponding public key that will be used by other nodes to verify VRF proof can be assessed so that it does not needs to be transmitted with $e_{u,r}$.
+
+Moreover, node~$u$ needs to wait for a fixed period~$\Delta$ (e.g., one second representing the network delay) before he endorses $s_r$.
+During this period, if $u$ received multiple block summaries from the same leader, it would endorse the one with minimal hash.
+Such a measure is designed to prevent a malicious leader to produce multiple block summaries to cause forks.}
 
